### 2019-08-19 chapters/4-approach.tex
Add introduction

\subsection{Constraints and restrictions}
The following section presents the restrictions that different type checkers perform on JavaScript code. The state of the art is shown through a comparison between \mintinline{text}{TypeScript}{TypeScript}, \mintinline{text}{Flow} and \mintinline{text}{Infernu}. All of them introduce the concept of restrictions for JS from different angles and for different use cases. The analysis is going to be performed on the \mintinline{text}{+} operator.

@@

\subsubsection{Flow}
Flow is a static type checker for JavaScript developed by Facebook \citep{flow}. It is intended to aid developers while writing JS code by detecting different errors. It only allows to use the \mintinline{text}{+} operator between \mintinline{text}{string} and \mintinline{text}{string}, \mintinline{text}{number} and \mintinline{text}{number} or \mintinline{text}{string} and \mintinline{text}{number}, as explained in \coderef{code:type-inference-constraints-flow}.

>>>>

\subsection{Constraints and restrictions}
The following section presents the restrictions that different type checkers perform on JavaScript code. The state of the art is shown through a comparison between \mintinline{text}{TypeScript}, \mintinline{text}{Flow} and \mintinline{text}{Infernu}. All of them introduce the concept of restrictions for JS from different angles and for different use cases. The analysis is going to be performed on the \mintinline{text}{+} operator.

@@

\subsubsection{Flow}
Flow is a static type checker for JavaScript developed by Facebook \citep{flow}\citep{FLOW_DBLP:journals/pacmpl/ChaudhuriVGRL17}. It is intended to aid developers while writing JS code by detecting different errors. It only allows to use the \mintinline{text}{+} operator between \mintinline{text}{string} and \mintinline{text}{string}, \mintinline{text}{number} and \mintinline{text}{number} or \mintinline{text}{string} and \mintinline{text}{number}, as explained in \coderef{code:type-inference-constraints-flow}.

### 2019-08-19 chapters/6-conclusions.tex
Add introduction

We exposed the fundamental aspect of capturing the developer's intention when inferring types in JavaScript. Instead of applying constraints and restrictions for operations with certain types, we presented a proposal where common practices are favored. Uncommon usage is not forbidden but greatly disfavored. Used in a first place merely as an initial code base for executing the library and approximating types, code examples turned out to be extremely useful for inferring types. They expose the developer's intention explicitly through code.

@@

>>>>

We exposed the fundamental aspect of capturing the developer's intention when inferring types in JavaScript. Instead of applying constraints and restrictions for operations with certain types, we presented a proposal where common practices are favored. Uncommon usage is not forbidden but greatly disfavored. Accordingly, we collected evidence regarding the usage of JavaScript operators by analyzing 400 libraries. Furthermore, used in a first place merely as an initial code base for executing the library and approximating types, code examples turned out to be extremely useful for inferring types. They expose the developer's intention explicitly through code.

@@

\draft{JAVERT!!}
